---
title: "regression_yl4606"
output: 
  html_document:
    toc: true
    toc_float: true
---
# Statistical Analysis

## Hypothesis
In this analysis, we are insterested in 

```{r setup, include = FALSE}
library(tidyverse)
library(purrr)
library(broom)
library(modelr)

knitr::opts_chunk$set(
  fig.width = 6, 
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

reading two datasets
```{r, warning = FALSE}
wine_150k = read_csv("./wine_data/winemag-data_first150k.csv")
conti_country = read_csv("./wine_data/country-and-continent-codes-list-csv_csv.csv")
```

a little bit tidying, add continent column to 150k wine data
```{r, warning = FALSE}
# wine data tidy
wine_150k = wine_150k %>% 
  janitor::clean_names() %>% 
  select(country, points, price, variety) %>% 
  mutate(country = factor(country),
         variety = factor(variety)) %>% 
  drop_na(country)

#conti_country data tidy
conti_country_tidy <- conti_country %>% 
  janitor::clean_names() %>% 
  separate(country_name, into = c("country", "prefix"), sep = ",") %>% 
  mutate(
    country = replace(country, country == "Slovakia (Slovak Republic)", "Slovakia"),
    country = replace(country, country == "United Kingdom of Great Britain & Northern Ireland", "England"),
    country = replace(country, country == "Korea", "South Korea"),
    country = replace(country, country == "United States of America", "US"),
  ) %>% ## standardize country names to do left_join
  select(continent_name, country) %>% 
  mutate(continent = as.factor(continent_name)) %>% 
  select(-continent_name)

rm(conti_country)

#left_join to wine data to get continent info, US-France row removed
wine_with_conti<-
  left_join(wine_150k, conti_country_tidy, by = ("country" = "country")) %>% 
  mutate(continent = fct_relevel(continent, "North America")) %>%  ##let US as the reference
  select(country, continent, everything()) %>% 
  drop_na(continent) 
```

# scatter plot: Price(Y) vs Points(X) by Variety(Z)
```{r}
# 632 unique varieties, select most frequent 4 vareties to fit the model
top_variety <- wine_with_conti %>% 
  group_by(variety) %>% 
  summarise(count = n()) %>% 
  arrange(desc(count)) %>% 
  filter(count>10000)

top_variety_list <- as.vector(top_variety$variety)

# wine_with_conti filtered
top_wine_with_conti<- 
  wine_with_conti %>% 
  filter(variety %in% top_variety_list) %>% 
  mutate(
    variety = fct_infreq(variety)
  ) ## most frequent variety as the reference

# scatter plot
top_wine_with_conti %>% 
  ggplot(aes(x = points, y = price, color = variety)) +
  geom_point(alpha = 0.5)+
  geom_smooth(method='lm')+
  ylim(0,750)
```

# test significance of interactions between points and variety: price ~ points*variety
```{r}
lm(price ~ points*variety, data = top_wine_with_conti) %>% 
  tidy()
```
There is a significant interaction between points and variety. It means that the relationship between points and price varies by different variety, especially between Pinot Noir and Chardonnay, Red Blend and Chardonnay.

# Stratified analysis: fit separate regression models by variety
```{r}
# nested within variety
nest_lm_res =
  top_wine_with_conti %>% 
  nest(data = -variety) %>% 
  mutate(
    models = map(data, ~lm(price ~ points, data = .x)),
    results = map(models, broom::tidy)) %>% 
  select(-data, -models) %>% 
  unnest(results)
nest_lm_res
```

```{r}
# price ~ points for stratified variety
nest_lm_res %>% 
  select(variety, term, estimate) %>% 
  mutate(term = fct_inorder(term)) %>% 
  pivot_wider(
    names_from = term, values_from = estimate) %>% 
  knitr::kable(digits = 3)
```


# Price(Y) vs. Points(X) * Variety(Z) + Continent(M) 

Is continent significant?
```{r}
# test significance of categorical predictor 'variety'
fit_null = lm(price ~ points * variety, data = top_wine_with_conti)
fit_alt = lm(price ~ points * variety + continent, data = top_wine_with_conti)

anova(fit_null, fit_alt) %>% 
  broom::tidy()  #p-val = 0
```
Yes. 

ANOVA TO check interaction

Then explain