---
title: "Reviews of Asian-Pacific Wines"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

```{r setup, include = FALSE}
library(tidyverse)
library(patchwork)
library(plotly)
library(flexdashboard)

knitr::opts_chunk$set(
	fig.width = 10, 
  fig.asp = .6,
  out.width = "100%"
)
```

<br/>

### Asian-Pacific Countries Comparison

```{r Asian-Pacific Countries Bar Plot, message = FALSE, warning = FALSE}
load("./data/wine150_tidy")

wine150_tidy %>% 
  select(country, points_avg_country) %>% 
  filter(country %in% c("Australia", "China", "Georgia", "India", "Israel", "Japan", "Lebanon", "New Zealand", "South Korea", "Turkey")) %>% 
  mutate(country = fct_reorder(country, desc(points_avg_country))) %>% 
  unique() %>% 
  mutate(text_label = str_c("Country: ", country, "\nAverage Points: ", points_avg_country)) %>% 
  plot_ly(
    x = ~country, y = ~points_avg_country, color = ~factor(country), text = ~text_label,
    type = "bar", colors = "viridis") %>%
  layout(
    xaxis = list(title = "Asian-Pacific Countries"),
    yaxis = list(title = "Average Wine Points", range = (c(80,88))),
    title = "Average Wine Points of Asian-Pacific Countries")
```

By comparing wine review data of the 10 countries in the Asian-Pacific region, we could see that Turkey has the highest average points (88.1) and South Korea has the lowest average points (81.5). There might be many explanations for this result. For grapes, the colder weather in South Korea may be less favorable than the warmer weather in Turkey. In addition, there may be a culture explanation. From the bar plot, we find that South Korea, China and Japan have the lowest average wine points, and according to the cultures of these three East Asian countries, wine is not even their most popular alcoholic beverage.

<br/>

### Top 20 Asian-Pacific Wineries

```{r Top 20 Asian-Pacific Wineries Box Plot, message = FALSE, warning = FALSE}
load("./data/wine150_tidy")

wine150_tidy %>% 
  select(points, country, winery, variety, points_avg_variety, points_avg_winery) %>% 
  filter(country %in% c("Australia", "China", "Georgia", "India", "Israel", "Japan", "Lebanon", "New Zealand", "South Korea", "Turkey")) %>% 
  mutate(winery = fct_reorder(winery, desc(points_avg_winery))) %>% 
  filter(as.numeric(winery) <= 20) %>% 
  arrange(winery) %>% 
  plot_ly(
    x = ~winery, y = ~points, color = ~factor(winery),
    type = "box", colors = "viridis") %>%
  layout(
    xaxis = list(title = "Asian-Pacific Wineries"),
    yaxis = list(title = "Wine Points"),
    title = "Top 20 Asian-Pacific Wineries: Highest Professional Recognition")
```

<br/>

### Bottom 20 Asian-Pacific Wineries

```{r Bottom 20 Asian-Pacific Wineries Box Plot, message = FALSE, warning = FALSE}
load("./data/wine150_tidy")

wine150_tidy %>% 
  select(points, country, winery, variety, points_avg_variety, points_avg_winery) %>% 
  filter(country %in% c("Australia", "China", "Georgia", "India", "Israel", "Japan", "Lebanon", "New Zealand", "South Korea", "Turkey")) %>% 
  mutate(winery = fct_reorder(winery, points_avg_winery)) %>% 
  filter(as.numeric(winery) <= 20) %>% 
  arrange(winery) %>% 
  plot_ly(
    x = ~winery, y = ~points, color = ~factor(winery),
    type = "box", colors = "viridis") %>%
  layout(
    xaxis = list(title = "Asian-Pacific Wineries"),
    yaxis = list(title = "Wine Points"),
    title = "Bottom 20 Asian-Pacific Wineries: Lowest Professional Recognition")
```

<br/>

### Top 10 Grapes for Asian-Pacific Wines

```{r Most Favorable Asian-Pacific Grapes Violin Plot, message = FALSE, warning = FALSE}
load("./data/wine150_tidy")

wine150_tidy %>% 
  select(points, country, winery, variety, points_med_variety, points_med_winery) %>% 
  filter(country %in% c("Australia", "China", "Georgia", "India", "Israel", "Japan", "Lebanon", "New Zealand", "South Korea", "Turkey")) %>% 
  mutate(variety = fct_reorder(variety, desc(points_med_variety))) %>% 
  filter(as.numeric(variety) <= 10) %>% 
  arrange(variety) %>% 
  plot_ly(
    x = ~variety, y = ~points, color = ~factor(variety),
    type = "violin", colors = "viridis") %>%
  layout(
    xaxis = list(title = "Grapes for Asian-Pacific Wines"),
    yaxis = list(title = "Wine Points"),
    title = "Most Favorable 10 Grapes for Asian-Pacific Wines: Highest Professional Recognition")
```

<br/>

### Bottom 10 Grapes for Asian-Pacific Wines

```{r Least Favorable Asian-Pacific Grapes Violin Plot, message = FALSE, warning = FALSE}
load("./data/wine150_tidy")

wine150_tidy %>% 
  select(points, country, winery, variety, points_med_variety, points_med_winery) %>% 
  filter(country %in% c("Australia", "China", "Georgia", "India", "Israel", "Japan", "Lebanon", "New Zealand", "South Korea", "Turkey")) %>% 
  mutate(variety = fct_reorder(variety, points_med_variety)) %>% 
  filter(as.numeric(variety) <= 10) %>% 
  arrange(variety) %>% 
  plot_ly(
    x = ~variety, y = ~points, color = ~factor(variety),
    type = "violin", colors = "viridis") %>%
  layout(
    xaxis = list(title = "Grapes for Asian-Pacific Wines"),
    yaxis = list(title = "Wine Points"),
    title = "Least Favorable 10 Grapes for Asian-Pacific Wines: Lowest Professional Recognition")
```

