---
title: "Tidy Wine Data"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)

knitr::opts_chunk$set(
	fig.width = 6, 
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

set.seed(1)
```

<br/>

### Import `winemag-data_first150k.csv` data.

```{r wine150_df, message = FALSE}
wine150_df = 
  read_csv("./data/winemag-data_first150k.csv") %>% 
  janitor::clean_names() %>% 
	select(id = x1, points, price, country, province, variety, winery) %>% 
  mutate(
		country = factor(country),
		province = factor(province),
		variety = factor(variety),
		winery = factor(winery)		
	)
```

The original dataset `winemag-data_first150k.csv` has `r nrow(wine150_df)` observations. <br/>
The numbers of missing values for some important variables are as follows. <br/>
`id`: `r sum(is.na(pull(wine150_df, id)))` missing observations. <br/>
`points`: `r sum(is.na(pull(wine150_df, points)))` missing observations. <br/>
`price`: `r sum(is.na(pull(wine150_df, price)))` missing observations. <br/>
`country`: `r sum(is.na(pull(wine150_df, country)))` missing observations. <br/>
`province`: `r sum(is.na(pull(wine150_df, province)))` missing observations. <br/>
`variety`: `r sum(is.na(pull(wine150_df, variety)))` missing observations. <br/>
`winery`: `r sum(is.na(pull(wine150_df, winery)))` missing observations. <br/>

<br/>
 
### Create average points and price at the country and province levels respectively for `winemag-data_first150k.csv` data.

```{r wine150_location}
wine150_tidy =
  wine150_df %>% 
  arrange(country, points) %>% 
  group_by(country) %>% 
  mutate(
    points_avg_country = round(mean(points), 2),
    points_med_country = median(points),
    price_avg_country = round(mean(price, na.rm = TRUE), 2),
    price_med_country = median(price)
  ) %>% 
  ungroup(country) %>% 
  arrange(province, points) %>% 
  group_by(province) %>% 
  mutate(
    points_avg_province = round(mean(points), 2),
    points_med_province = median(points),
    price_avg_province = round(mean(price, na.rm = TRUE), 2),
    price_med_province = median(price)
  ) %>% 
  ungroup(province) %>%  
  arrange(country, province, points)
```

Due to 5 missing values of country and province in `winemag-data_first150k.csv` data, average points and price are also created for this missing group. Caution is needed for subsequent analysis.

<br/>

### Create average points and price at the variety and winery levels respectively for `winemag-data_first150k.csv` data.

```{r wine150_variety_winery}
wine150_tidy =
  wine150_tidy %>% 
  arrange(variety, points) %>% 
  group_by(variety) %>% 
  mutate(
    points_avg_variety = round(mean(points), 2),
    points_med_variety = median(points),
    price_avg_variety = round(mean(price, na.rm = TRUE), 2),
    price_med_variety = median(price)
  ) %>% 
  ungroup(variety) %>% 
  arrange(winery, points) %>% 
  group_by(winery) %>% 
  mutate(
    points_avg_winery = round(mean(points), 2),
    points_med_winery = median(points),  
    price_avg_winery = round(mean(price, na.rm = TRUE), 2),
    price_med_winery = median(price)
  ) %>% 
  ungroup(winery) %>%    
  arrange(variety, winery, points)

save(wine150_tidy, file = "./data/wine150_tidy")
```

There is not any missing value of variety in `winemag-data_first150k.csv` data.

